---
title: "Plotly Example - Developing Data Products"
author: "Chris Rector"
date: "January 22, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Overview

This document was created for the week 3 course project for the Johns Hopkins Developing Data Products course on Coursera. It demonstrates the use of the Plotly library and the sharing of data visualizations through HTML.

Here we plot the sum of home sales per month of the year in the province of Nova Scotia (Canada), using data from the DataZone open data portal: https://www.thedatazone.ca/Assessment/Parcel-Sales-History/6a95-ppg4.


```{r dataload, echo=TRUE, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)
library(scales)

d <- read.table("c:/tmp/Parcel_Sales_History.tsv", sep="\t", header=TRUE, quote="", comment.char="")
datetime <- strptime(factor(d$Sale.Date),  format = "%B %d %Y")
d <- cbind(d, datetime)
year <- as.numeric(format(d$datetime, "%Y"))
d <- cbind(d, year)
month_num <- as.numeric(format(d$datetime, "%m"))
d <- cbind(d, month_num)

d$price <- as.numeric(d$Sale.Price)

dt <- aggregate(price ~ month_num, sum, data=d)
```

## Plotly

Here we use plotly to plot the sum of home sales in each month (1=January).

```{r viz, echo=TRUE, message=FALSE, warning=FALSE}

plot_ly(x=dt$month_num, y=dt$price, type="scatter", mode="lines")


```


