---
title: "Plotly Presentation"
author: "Chris Rector"
date: "January 25, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This document was created for the week 3 course project for the Johns Hopkins Developing Data Products course on Coursera. It demonstrates the use of the Plotly library and the sharing of data visualizations through HTML.


```{r dataload, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)
library(scales)

d <- read.table("c:/tmp/Parcel_Sales_History.tsv", sep="\t", header=TRUE, quote="", comment.char="")
datetime <- strptime(factor(d$Sale.Date),  format = "%B %d %Y")
d <- cbind(d, datetime)
year <- as.numeric(format(d$datetime, "%Y"))
d <- cbind(d, year)
month_num <- as.numeric(format(d$datetime, "%m"))
d <- cbind(d, month_num)

d$price <- as.numeric(d$Sale.Price)

dt <- aggregate(price ~ month_num, sum, data=d)
```

## Data Used in This Assignment

- We plot the sum of home sales per month of the year in the province of Nova Scotia (Canada)
- We used data from the DataZone open data portal: https://www.thedatazone.ca/Assessment/Parcel-Sales-History/6a95-ppg4.
- the plot shows total home sales in each month (1=January).


## Plotly Plot


```{r viz, echo=TRUE, message=FALSE, warning=FALSE}

plot_ly(x=dt$month_num, y=dt$price, type="scatter", mode="lines")

```

